Notes on Big MRA

### 2018-05-14 TEX/notes_will/notes_moments/backups/test5_save9.tex
updates on section 2

Because likelihood methods are computationally expensive, methods based on recovery from moments and cumulants, which are akin to our method, have also been previously used for system identification. The question of identifiablity of $x$ from third-order statistics with non-Gaussian $W$ was considered in \cite{lii1982deconvolution}. A method using fourth-order cumulants is described in \cite{tugnait1984id}, while a method using fourth-order cumulants is described in \cite{giannakis1989id}.

>>>>

Because likelihood methods are computationally expensive, methods based on recovery from moments and cumulants, which are akin to our method, have also been previously used for system identification. The question of identifiablity of $x$ from third-order statistics with non-Gaussian $W$ was considered in \cite{lii1982deconvolution}. A method using third-order cumulants is described in \cite{giannakis1989id}, while a method using fourth-order cumulants is described in \cite{tugnait1984id}.

### 2018-05-14 TEX/notes_will/notes_moments/notes.tex
updates on section 2

Our problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, we observe a length $n$ signal $Y$ given by:
%
\begin{align}
%
    Y = x \ast W + \ep,
%
\end{align}
%
where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise. The goal of this problem is to estimate the ``system'' vector $x$. Specializing to the case where $W$ is a random sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.

@@

Other problems solve for parameterized models of $x$; for instance, see \cite{andrieu2001bayesian}. This paper also considers multiple distinct signals $x$ embedded in the same observation vector $Y$, as in our heterogeneity framework. Their proposed solution is a Markov Chain Monte Carlo algorithm designed for their specific parametrized problem.

Because likelihood methods are computationally expensive, methods based on recovery from moments and cumulants, which are akin to our method, have also been previously used for system identification. The question of identifiablity of $x$ from third-order statistics with non-Gaussian $W$ was considered in \cite{lii1982deconvolution}. A method using third-order cumulants is described in \cite{giannakis1989id}, while a method using fourth-order cumulants is described in \cite{tugnait1984id}.

>>>>

Our problem can be interpreted as a special case of the problem of ``system identification'' in the field of signal processing. In this class of problems, we observe a length $n$ signal $Y$ given by:
%
\begin{align}
%
    Y = x \ast W + \ep,
%
\end{align}
%
where $x$ is an unknown linear filter of length $L$; $W$ is an unknown random ``input'' sequence; and $\ep$ is random additive noise. The problem has also been studied in the case of a known input $W$ \cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}.  The goal of this problem is to estimate the ``system'' vector $x$. The question of identifiability of $x$ under this observation model is addressed for certain non-Gaussian $W$ in \cite{benveniste1980}, and for certain Gaussian inputs $W$ in \cite{kormylo1983id}. In the special case where $W$ is a random, unknown sequence of spikes satisfying the spacing requirement we obtain our model in the $K=1$ case of a single vector.

@@

Other problems solve for parameterized models of $x$; for instance, see \cite{andrieu2001bayesian}. That same paper also considers multiple distinct signals $x$ embedded in the same observation vector $Y$, as in our heterogeneity framework. Their proposed solution is a Markov Chain Monte Carlo algorithm designed for their specific parametrized problem.

Because likelihood methods are computationally expensive, methods based on recovery from moments and cumulants, which are akin to our method, have also been previously used for system identification. The question of identifiablity of $x$ from third-order statistics with non-Gaussian $W$ was considered in \cite{lii1982deconvolution}. A method using fourth-order cumulants is described in \cite{tugnait1984id}, while a method using third-order cumulants is described in \cite{giannakis1989id}.

%%%All these papers note that in general, it is not possible to recover $x$ from second-order statistics alone, since the phase information is lost.
